Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-27 CAV 2025 TODO/Comparison.tex
update

First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP. Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP. They both work by backpropagating gradients vectors $\bm{\bar{\lambda}}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected. To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be $r(\bm{u}_k)=\frac{\UB(\bm{u}_k)}{\UB(\bm{u}_k)-\LB(\bm{u}_k)}$.

\begin{align*}
\bm{\bar{\lambda}}_{n-1} = -W^T_n\bm{1}, \hspace*{4ex}  	\bm{\bar{\lambda}}_{k-1} = W^T_k\big(\dfrac{[\hat{\bm{u}_k}]_+}{[\hat{\bm{u}_k}]_+-[\hat{\bm{l}_k}]_-}\odot\bm{\bar{\lambda}}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
\end{align*}

>>>>

First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP. Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP. They both work by backpropagating gradients vectors $\bm{\lambda}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected. To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be $r(\bm{u}_k)=\frac{\UB(\bm{u}_k)}{\UB(\bm{u}_k)-\LB(\bm{u}_k)}$.

\begin{align*}
\bm{\lambda}_{n-1} = -W^T_n\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = W^T_k\big(\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))}\odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
\end{align*}
